### 2015-12-08 intro.tex
cheers

\section{Introduction}
\paragraph{Basic issues. }
\begin{itemize}
\item [NY] formalize and investigate a security notion of limited interest
\item The proposed construction won’t scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\end{itemize}

@@

\begin{itemize}
\item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature. (See wikipedia, a section of which I’ve pasted in at the end of this doc.)
\item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
\item Establish security notions that are appropriate for broader use cases (e.g. privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
\item Develop constructions that are secure and are supported by a practice-informed argument for deployment
\item Expand from Bloom filters to “Approximate Set Membership” primitives, i.e. more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e. it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
\end{itemize}

>>>>

\section{Introduction}
\paragraph{Basic issues. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won’t scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\end{itemize}

@@

\begin{itemize}
\item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature. (See wikipedia, a section of which I’ve pasted in at the end of this doc.)
\item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
\item Establish security notions that are appropriate for broader use cases (e.g. privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
\item Develop constructions that are secure and are supported by a practice-informed argument for deployment
\item Expand from Bloom filters to “Approximate Set Membership” primitives, i.e. more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e. it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
\item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.  Note: this should be done only if it makes sense -- i.e. it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
\end{itemize}
